%-------------------------------------------------------------------------------
\section{Evaluation}
%-------------------------------------------------------------------------------
We evaluate \sys{} on two metrics: (1) can desired decorrelation policies be easily specified using the
provided decorrelation primitives for a range of practical applications?, and (2) can decorrelation
be supported with low performance overhead?

Our evaluation exemplifies how a suite of applications (Lobste.rs, \lyt{TODO}) can express a diverse
range of privacy policies using \sys{} with low developer effort with low overhead.

\subsection{Example policies}
\begin{figure}
\begin{lstlisting}[language=Rust]
use GhostColumnPolicy, GeneratePolicy;
let ghost_policies = GhostGenerationPolicy::new(
  ("users", 
     [("id", Generate(Random)),
     ("username", Generate(Random)),
     ("karma", Generate(Default(0)))]),
  ...);

let edge_policies = vec![
  KeyRelationship{
    child: "stories".to_string(),
    parent: "users".to_string(),
    column_name: "user_id".to_string(),
    parent_child_decorrelation_policy: Decor,
    child_parent_decorrelation_policy: NoDecorRetain,
  },
  KeyRelationship{
    child: "taggings".to_string(),
    parent: "tags".to_string(),
    column_name: "tag_id".to_string(),
    parent_child_decorrelation_policy: 
        NoDecorSensitivity(0.25),
    child_parent_decorrelation_policy: NoDecorRetain,
  },
  ...];

 ApplicationPolicy {
    entity_type_to_decorrelate: "users",
    ghost_policies: ghost_policies,
    edge_policies: edge_policies,
 }
\end{lstlisting}
    \label{fig:policy}
    \caption{Excerpt of the Lobsters Application Policy}
\end{figure}
We provide several variants of an application policy for Lobsters. Each requires specifying at most 17 key
relationships and at most 5 ghost entity generation policies (see Figure~\ref{fig:policy} for an example
of what these policies). The total number of lines that a developer must write range from \lyt{TODO}
to \lyt{TODO} LoC (current policy is 190LoC).

We also evaluate policies for several other applications: (1) an Instagram clone with posts, likes,
hashtags, shares, and groups; (2) PrestaShop, an open-source e-commerce web application; and (3)
\lyt{I would like to go HotCrp here... will try and get something here before we meet tomorrow}

\paragraph{Lobsters}

The first policy replicates what the behavior of the current Lobsters deployment upon user
unsubscription, with the exception that users are replaced with ghost users rather than a global
placeholder. This requires specifying \texttt{Decorrelate} policies for all edges from entities with users
as parents, resulting in the developer writing 9 edge policies and one ghost generation policy (for
ghost users). While this policy does nothing significant, splitting a user into multiple ghosts as
compared to a global placeholder allows the user to resubscribe by identifying their ghost
counterparts, whereas a global placeholder does not. Furthermore, splitting users into multiple
users as compared to grouping them together upon unsubscription may benefit privacy: global
placeholder users indicate that any child of the placeholder belongs to some deleted user, whereas
ghost users may more successfully mask which children have been abandoned.

The second policy decorrelates all user-related edges, but additionally desensitizes tags so the
taggings associated with sensitive stories are at most 25\% the number of stories with that tag.
Ghost stories clone randomly chosen existing stories with slight variations on the url.
This limits the amount that an observer can determine that a particular story was posted by a
particular user simply by knowing that a certain user has posted about the tag topic (e.g.,\ a researcher 
in visualization). However, Lobsters still retains the content of these tagged stories.

\lyt{TODO} third policy.
\paragraph{PrestaShop.} 
PrestaShop entities include customers, products, orders, carriers, employees, and shops (as well as
many other entities such as product categories, languages, countries, shopping cart, etc.) There are
214 total different entities. 

Due to the large scope of the schema, we automatically generate policies for the 324 key relationships between them 
with \texttt{NoDecorrelation:Retain} policies, which means that \sys{} does, by default, no work upon
decorrelation and recorrelation. (We could also imagine that a \texttt{Decorrelate} or
\texttt{NoDecorrelate:Remove} policy could be
the default here, but we choose a policy by default that will not break application semantics,
instead of a policy that provides the strongest possible unsubscription privacy).

By simply providing a ghost customer generation policy and modifying all key relationships with
customer parents to \texttt{Decorrelate} or \texttt{Remove} policies, PrestaShop can ensure that
customer information is appropriately de-identified when a customer unsubscribes.
Currently, PrestaShop has explicit GDPR policies for its merchants when a customer requests to delete
their account: their personal account details (age, email, address) are removed, but order invoices
and abandoned carts are transferred to an anonymous account
\lyt{TODO \url{https://doc.prestashop.com/display/PS17/Complying+with+the+GDPR}}.
\sys{} allows PrestaShop to go beyond pseudonymity, creating individual (ghost) accounts for each
cart and order invoices of a customer, and also allowing a customer to retrieve these orders and
abandoned carts if she rejoins the application.

\sys{} also can help PrestaShop keep attributes such as the country or language of a user for
statistical analyses (used by merchants to analyze product popularity). Ghost customers can generate
links to countries nearby a set of countries similar to the original user; if this still reveals too
much sensitive information, the location can be desensitized (adding additional generated ghost
customers not related to the original user for noise).

This process requires going through each of the individual key relationships, which must be done to
generate the schema in the first place.

\paragraph{HotCRP.}

\subsection{Performance}
\paragraph{Experimental Setup.}
The performance experiments reported are run on Intel Xeon E5-2660 v3 CPUs, with a
single-threaded client and \sys{}'s shim layer each pinned to a single core. \sys{} runs on top of 
MariaDB (v10.4.13). 

We compare the application execution performance on four systems, all of which configure MariaDB to
store the database on a ramdisk to avoid disk IO overheads.
\begin{enumerate}
    \item \texttt{NoShim}: queries are directly issued to a MariaDB instance;
    \item \texttt{Shim}: queries are intercepted by the shim layer,
        which does nothing more than send queries to the MariaDB instance and
        return the results back to the client;
    \item \texttt{ShimParsing}: queries are intercepted the shim layer, parsed into a
        SQL AST (which is discarded), and then sent to the MariaDB instance; the shim then returns the results to the
        client. 
    \item \texttt{\sys{}}: queries are intercepted by the shim layer and parsed into a SQL AST. \sys{}
        then processes the parsed query, potentially introducing ghost entities and sending additional queries to the MariaDB backend.
        \sys{} then returns results to the client.
\end{enumerate}

We compare \texttt{NoShim} and \texttt{Shim} to define the cost of query interception; \texttt{Shim}
and \texttt{ShimParsing} to define the cost of query parsing; and \texttt{ShimParsing} and
\texttt{\sys{}} to define the cost of adding decorrelation and recorrelation support.  \texttt{Shim}
provides an upper bound for \sys{}'s (single-threaded) performance, as the costs of query parsing
and decorrelation are not necessarily fundamental.

\paragraph{Lobste.rs Performance}
\sys{} utilizes the trawler workload~\cite{trawler} for Lobsters, which emulates production
Lobsters traffic according to a recorded production workload. The database initially begins with 3K
users, 20K stories, and 60K comments (1/2 the size of the the real Lobsters deployment), and issues
queries according to the recorded traffic distribution. The query distribution skews towards reads
(recent and frontpage stories) over writes (votes, commenting, and posting of stories); the
workload assumes that users with popular content are also more active and likely to post stories,
comment, and vote.

The benchmarks perform 10000 actions, each performing on average 8 application queries. 
We measure (1) overall throughput, (2) the distribution of application query
latencies, (3) the query multiplication per application query performed by \sys{}, and (4) the
storage cost (in-memory and on-disk).

The first benchmark measures \sys{}'s performance during \emph{normal execution}, namely when only
read and update actions performed by Lobsters are executed. 
The second benchmark measures \sys{}'s performance with 10\% of the actions being unsubscription. If
an unsubscribed user is chosen to perform an action, this user is first resubscribed.
\texttt{NoShim}, \texttt{Shim}, and \texttt{ShimParsing} simply delete or insert the chosen user on
unsubscription or resubscription respectively; this provides a very conservative estimate of the
amount of work these baseline systems would need to do if a user withdrew their data from the system.

\lyt{Currently debugging the benchmark... (some error with repeat keys, hopefully won't take too long)}
To complete 10K actions during normal execution, \texttt{NoShim} takes TODO, \texttt{ShimOnly} takes
TODO, \texttt{ShimParse}
takes TODO; and \texttt{\sys{}} takes 185s.
We show the latency results of the 3 different Lobsters policies described above in
Figure~\ref{fig:results}. 
\lyt{TODO memory usage}

To complete 10K actions during normal execution, \texttt{NoShim} takes 263s, \texttt{ShimOnly} takes 277s, \texttt{ShimParse}
takes 284s; and \texttt{\sys{}} takes TODO.
\lyt{TODO memory usage}
