%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Template for USENIX papers.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{usenix-2020-09}

% to be able to draw some self-contained figs
\usepackage{tikz}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage[normalem]{ulem}
\usepackage{listings, listings-rust}

\newcommand{\sys}{DeCor} 
\newcommand{\plinked}{$p_\text{linked}$} 
\newcommand{\premnant}{$p_\text{remnant}$} 
\newcommand{\uidkey}{$uid_\text{key}$} 
\newcommand{\gidkey}{$gid_\text{key}$} 
\newcommand\lyt[1]{\textcolor{green!55!blue}{[lyt: {#1}]}}
\newcommand{\tabitem}{~~\llap{\textbullet}~~}
%\renewcommand\lyt[1]{}

\definecolor{codegreen}{rgb}{0,0.4,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}

\lstdefinestyle{rust}{
    %backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\scriptsize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=3pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2
}
\lstset{style=rust}

%-------------------------------------------------------------------------------
\begin{document}
%-------------------------------------------------------------------------------

%don't want date printed
\date{}

% make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{\Large \bf \sys{}: Ensuring the Right To Be Forgotten (and Remembered) in Web Applications}

%for single author (just remove % characters)
%\author{
%{\rm Lillian Tsai}\\
%MIT
%\and
%{\rm Malte Schwarzkopf}\\
%Brown University
%% copy the following lines to add more authors
%\and
%{\rm Eddie Kohler}\\
%Harvard University
%} % end author

\author{
{\rm Anonymous Authors}\\
} % end author

\maketitle

%-------------------------------------------------------------------------------
\begin{abstract}
%-------------------------------------------------------------------------------
Web services increasingly face legal requirements to protect users' privacy (e.g.,\ the GDPR). These
    laws require companies to properly delete and anonymize users’ data when a user requests to
    remove their data. And beyond current legal requirements, many users would rest easier if they
    knew that they can unsubscribe from a web service at any time, without losing their data and
    with the opportunity to come back later.

    But unsubscribing users without compromising either the leaving user's privacy or the application
    experience for the remaining users is difficult. Removing too much information meets privacy
    requirements, but may yield surprising application behavior (e.g.,\ disappearing content);
    removing too little risks exposing the identity of unsubscribed users via inference attacks.

    In this paper, we propose \sys{}, a new system for safe unsubscription and resubscription of
    users in database-backed web services. \sys{} helps application developers specify fine-grained
    privacy policies to meet de-identification requirements, and goes beyond: with \sys{}, it is
    possible for users to switch between a privacy-preserving unsubscribed mode and an
    identity-revealing subscribed mode at any time without permanently losing their data. This
    facilitates important new web service paradigms, such as users granting a time-limited "lease"
    of data to a service instead of having a permanent service account.  
\end{abstract}

\input{intro}
\input{related}
\input{design}
\input{impl}
\input{eval}
\input{disc}

%-------------------------------------------------------------------------------
\section*{Acknowledgments}
%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
\section*{Availability}
%-------------------------------------------------------------------------------

\lyt{USENIX program committees give extra points to submissions that are
backed by artifacts that are publicly available. If you made your code
or data available, it's worth mentioning this fact in a dedicated
section.}

%-------------------------------------------------------------------------------
\bibliographystyle{plain}
\bibliography{paper}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%  LocalWords:  endnotes includegraphics fread ptr nobj noindent
%%  LocalWords:  pdflatex acks
