%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Disguising and Revealing Semantics}
\label{sec:comp}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
This section describes the semantics of disguising provided by \sys. 
In particular, we describe the end state of a data object given some history of disguise
applications and reveals.

\vspace{6pt}\noindent\textbf{\emph{Some Notation.}} We describe disguise histories as a list of
\app{d_i} and \rev{d_i} actions, where \app{d_i} corresponds to the application of disguise $d_i$, and
\rev{d_i} corresponds to the reveal of $d_i$'s diffs. Time moves to the right in the list.

For every data object $x$ in the system, \xstart describes its initial state, and
\xhist{[\app{d_1}, \dots]} describes its state after \sys has applied the history [\app{d_1},
$\dots$].


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{6pt}\noindent\textbf{\emph{Composing Multiple Disguise Applications.}}
Let $d_1$ and $d_2$ be two disguises, where $d_1$ is applied after $d_2$.
to produce disguise history [\app{d_1}, \app{d_2}]. 
%
Let $x$ be some application data object, where \xstart is its initial state, and
\xhist{[\app{d_1}, \app{d_2}]} is the final state after \sys applies $d_1$ and $d_2$.
%
If both $d_1$ and $d_2$ update $x$, what is \xhist{[\app{d_1}, \app{d_2}]}?
We consider two possible end states: 
%
\begin{enumerate}
    \item[(\appcompone)] \xhist{[\app{d_1}, \app{d_2}]} reflects the application of
        \emph{both $d_1$ and $d_2$} to \xstart. 

        In other words, if an \op{d_2}'s predicate \texttt{pred} matches \xstart, then \op{d_2} is
        applied to \xhist[\app{d_1}], even if \texttt{pred} does not match
        \xhist{[\app{d_1}]}. 

    \op{d_2} updates are applied sequentially after $d_1$'s updates if the two modify the
        same object attribute.

\item[(\appcomptwo)] \xhist{[\app{d_1}, \app{d_2}]} reflects the application of $d_1$ to \xstart, followed
by the application of $d_2$ to \xhist{[\app{d_1}]}. When deciding whether to apply to $x$,
        \sys matches \op{d_2}'s predicate only against
\xhist{[\app{d_1}]}, and not against the original state \xstart.
\end{enumerate}

\noindent
For example, let \op{d_1} decorrelate all posts from authors predicated on \texttt{author =
Bea}, and let \op{d_2} remove all posts predicated on \texttt{author = Bea}.
%
\begin{enumerate}
\item[(\appcompone)] Both \op{d_1} and \op{d_2} update posts originally having author ``Bea'', resulting in the
removal of all posts originally with author Bea.

\item[(\appcomptwo)] Applying \op{d_1} results in all posts with author ``Bea'' having
pseudoprinicipal authors such as ``anonFox.'' \op{d_2} only knows the state of posts after
\op{d_1} occurs, and does not remove any posts because no post has author ``Bea''.
\end{enumerate}

The choice of whether \xhist{[\app{d_1}, \app{d_2}]} should result in \appcompone or \appcomptwo depends on the
specific application and is left to the developer to specify. 

In certain scenarios, however, \sys can only achieve end state \appcomptwo. In order to achieve \appcompone,
$d_2$ must evalute predicates against \xstart, which requires knowing the value of \xstart.  To learn
\xstart, \sys must know how $d_1$ modified $x$ (\eg knowing that a post with author ``anonFox''
originally was a post with author ``Bea''); this information, however, is stored in in the diffs produced
by $d_1$. 

\sys may not have access to these diffs when applying $d_2$: a client who invokes $d_2$ while authenticated as
principal $q \neq p$, and who does not provide the relevant capabilities%y pairs \pcapa{pd_1}, 
cannot access $p$'s diffs for $d_1$. 

In this case, $d_2$ can only match against \xhist{[\app{d_1}]} and achieve end state \appcomptwo.
This is shown in Table~\ref{tab:composeapp}.

\begin{table}[h]
\centering
\begin{tabular}{ c | c c }
    & \multicolumn{2}{c}{\textbf{Access $d_1$'s diffs while \app{d_2}?}}\\
    & \textbf{Yes} & \textbf{No} \\
\hline
    \xhist{[\app{d_1},\app{d_2}]}& \appcompone or \appcomptwo & \appcomptwo 
\end{tabular}
\vspace{6pt}

\caption{Possibilities for \xhist{[\app{d_1},\app{d_2}]} depending on whether \sys has access to diffs from $d_1$ regarding $x$.}
\label{tab:composeapp}
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{6pt}\noindent\textbf{\emph{Semantics of Disguise Reversals.}}
We now consider composition of disguises in the presence of disguise reversals.

\begin{table}[h]
\centering
\begin{tabular}{ c | c c }
    & \multicolumn{2}{c}{\textbf{Access to $d_i$'s diffs while \app{d_i}?}}\\
    & \textbf{Yes} & \textbf{No} \\
\hline
    \xhist{[\app{d_i},\rev{d_i}]} & \xstart & \xhist{[\app{d_i}]}
\end{tabular}
\vspace{6pt}

\caption{Possibilities for \xhist{[\app{d_i},\rev{d_i}]} depending on whether \sys has 
    access to diffs from $d_i$ regarding $x$.}
\label{tab:composeapprev}
\end{table}

We first consider \textbf{\xhist{[\app{d_i},\rev{d_i}]}}; Table~\ref{tab:composeapprev}
illustrates how this state depends the authorization a client invoking \rev{d_i} provides to
\sys to access $d_i$'s diffs for $x$.
As expected, the updates applied by $d_i$ to $x$ cannot be revealed when the relevant diffs are
inaccessible.

\begin{table}[h]
\centering
\begin{tabular}{ c | c c }
    \textbf{$d_1$ and $d_2$'s Updates} & \multicolumn{2}{c}{\textbf{Access 
        to $d_1$'s diffs while \rev{d_1}?}}\\
    & \textbf{Yes} & \textbf{No} \\
    \hline
    \textbf{Independent} & \xhist{[\app{d_2}]} & \xhist{[\app{d_1},\app{d_2}]}\\
    \textbf{Conflict} & \xhist{[\app{d_1},\app{d_2}]} & \xhist{[\app{d_1},\app{d_2}]}
\end{tabular}
\vspace{6pt}
    \caption{\xhist{[\app{d_1},\app{d_2},\rev{d_1}]} depending on whether \sys has
    access to $d_1$'s diffs when revealing $d_1$, and whether updates from $d_1$ and
    $d_2$ to $x$ modify the same data.}
\label{tab:composeapprev1}
\end{table}

We next consider \textbf{\xhist{[\app{d_1},\app{d_2},\rev{d_1}]}}: the end state of $x$ when a disguise
$d_1$ is revealed after a subsequent disguise $d_2$ has been applied. 
Table~\ref{tab:composeapprev1} illustrates how the result
depends on \sys's access to $d_1$ diffs, and whether $d_1$ and $d_2$ performed
conflicting modifications to $x$'s attributes.

When the client invoking \rev{d_1} provides no authorization to access to $d_1$'s diffs, then the
updates applied by $d_1$ to $x$ cannot be revealed.  However, even if the client 
grants access to $d_1$'s diffs, \sys will fail to reveal $d_1$'s updates to $x$ if $d_2$ and $d_1$
both modify $x$ in a conflicting manner: $\rev{d_1}$ must not restore data that was also disguised by
$d_2$, and until $d_2$ is revealed, invocations of \rev{d_1} will not reveal \xstart.

\subsection{Composition Implementation Techniques}
\sys's algorithm for disguising and disguise reversal in most scenarios is straightforward. 

To apply disguise $d_i$, \sys applies each \op{d_i} to all
data objects satisfying \op{d_i}'s predicate, while also taking into account the information in
accessible diffs(to \eg predicate against undisguised versions of objects). Each \op{d_i} produces
one or more diffs, which \sys stores either globally or encrypted by a data capability at
\lcapa{pi_i}.

To reveal disguise $d_i$, \sys reveals the undisguised version of data stored in
accessible diffs corresponding to $d_i$ by updating the relevant objects $x$ in the database.

However, \sys must be careful of two potential problems:
(1) \sys cannot accidentally reveal data that must be disguised; and (2) \sys cannot let global
diffs recording updates to data $x$ leak information if $x$ is subsequently (privately) disguised.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{6pt}\noindent\textbf{\emph{Preventing Accidental Data Revelation.}}
\sys records the disguised state of data $x$ in each \tdiff{pd} recording a update performed by $d_i$
to $x$. If the state of $x$ does not match the disguised state in $d_i$'s diff for $x$, then \sys
knows the diff records a stale and overwritten update to $x$, and refuses to reveal the undisguised state of $x$
stored in the diff.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{6pt}\noindent\textbf{\emph{Preventing Global Diff Information Leakage.}}
%The ONLY REASON we need to update diffs is if they're global!!! If they're private, we can use the
%retroactive application method... (optimization to update our "own" diffs though)
%
A disguise may optionally store diffs in global storage, accessible to \sys without any client
authorization.
Such a global disguise provides no privacy guarantees against an adversary who compromises 
the application server, but does transform the application database so external users see disguised
data.

If $d_1$ is a global disguise and $d_2$ a normal, privacy-preserving disguise,
\op{d_2} may update a data object $x$ previously updated by \op{d_1}. 

\op{d_1} produces a global diff \tdiff{pd_1}; \op{d_2} produces a normal,
encrypted and secured diff \tdiff{pd_2}.

If \sys simply performs \op{d_2}'s update to $x$, an adversary can still read undisguised data
from the \tdiff{pd_1} diff because the diff is global and records a now-stale state of $x$!
%
To prevent global diffs like \tdiff{pd_1} from leaking data that should be disguised, \sys
updates the data in \tdiff{pd_1} with \op{d_2}'s update. An update to a diff such as
\tdiff{pd_1} itself generates a (private) diff \tdiff{pd_2}, just as updating a data
object generates a diff.

Revealing $d_2$ uses \tdiff{pd_2} to reveal the modification to \tdiff{pd_1}. 
If $d_1$ has already been revealed, and the database state of $x$ updated to reflect the
contents of \tdiff{pd_1} (which were updated by the application of $d_2$), then \sys
simply uses \tdiff{pd_2} to reveal the current state of $x$ in the database. 

If a future $d_3$ has further updated \tdiff{pd_1} in a way that conflicts with $d_2$'s update, then
upon reversal of $d_2$, \sys will notice that \tdiff{pd_2} records an overwritten update to
\tdiff{pd_1}, and will not revert the state of \tdiff{pd_1} until the future disguise $d_3$ has been
revealed .

\lyt{Note that removal is just an interesting case of this, in which \tdiff{pd_1} is removed, by a
diff \tdiff{pd_2} stored in \lcapa{pd_2} that saves the removal of \tdiff{pd_1} for reversal.}

%\vspace{6pt}\noindent\textbf{\emph{diff Modification for Object Identification.}}
%diffs need to refer to the correct objects even if objects have been modified by future disguises.
%Prior diffs should be revised by future disguises so that they apply correctly to the disguised
%data.
%This allows an earlier disguise to be revealed correctly.
%An easy way to avoid needing to do this is to have all objects in the DB have unique, permanent
%identifiers.
