%-------------------------------------------------------------------------------
\section{Discussion and Future Work}
%-------------------------------------------------------------------------------

\iffalse
\subsection{Limitations}

Like all applications that provide some type of post-unsubscription privacy guarantees, \sys assumes
that an adversary who aims to relink decorrelated entities to unsubscribed users, is limited in the
following ways:
\begin{itemize}
    \item An adversary can perform only those queries allowed by the application API,
i.e.,\ can access the application only via its public interface.
%\lyt{Alternatively, an adversary could perform arbitrary queries on some public subset of the
%application schema (e.g., all tables other than the mapping table, or all tables marked with some
%compliance policy); arbitrary queries over the
%entirety of the table are out of scope, unless ``private'' tables are removed and stored by
%unsubscribing users.}

    \item An adversary cannot perform application queries to the past or search web archives:
    information from prior application snapshots may reveal
    exactly how data records were decorrelated from unsubscribed users.

    \item An adversary cannot gain identifying information from re-shared or arbitrary
        user-generated content (for example, a reposted screenshot, or text in user stories or
        comments) that developers have left unghosted. 
        \sys gives developers the option to specify that unsubscription removes or replaces
        user-generated data and application metadata (e.g., date of postings, database ID columns),
        at the cost of losing this data.
\end{itemize}

User key / encrypted data storage scheme relies on application wanting to store user data (wanting
users to return). Also requires user to have some trusted third party.

Other limitations: 
single-threaded;
recovery / eventual consistency during un/resubscribe;
subset of MySql;
no support for schema updates / updates to policy

\subsection{Future work.}
\paragraph{Maintaining Aggregate Accuracy.}
As future work, \sys{} can optionally allow for entities to be decorrelated without affecting queries which
specifically return aggregation results.

Queries that specifically perform aggregations and return statistical measures (e.g.,
the count of number of users in the system, or the number of stories per user), can return
significantly different results. This affects the utility of the data for the application: for
example, if the application relies on the number of stories per tag to determine hot topics, these
would be heavily changed if ghost tags were created.  In addition, the adversary may learn which
entities are ghosts: for example, an abnormally low count of stories per tag might indicate to an
adversary that these tags are ghost tags.  \lyt{But perhaps it's ok if an adversary can tell what's
a ghost, as long as it can't tell which user each ghost is correlated with.}

\sys{} stores and separately updates answers to aggregation queries;
these answers are updated when queries update the data tables, and these queries do not read from
the application tables (which may contain ghost records).

An alternate solution might analyze the aggregations performed by application queries, and then
introduce ghosts that lead to the same (or close-enough) aggregation result. For example, if a tag
is split into ghost tags, one per story associated with the tag, but the application still would
like the count of stories for this tag to be high, one of the ghost tags can be populated with many
ghost stories to retain the count of stories per tag.  \sys{} would remove any ghost stories that
were created upon recorrelation. Note that this solution 1) requires that generating ghosts is
admissible, and 2) may be impossible for certain combinations of aggregations (e.g., queries that
return both the average stories per tag and also the total number of stories).

\lyt{I don't *think* differential privacy really should be applied here, because we'd also face the
issue of running out of privacy budget. Adding noise might ensure that the impact of any one
(real/ghost) user is very little, but it has its own noise/utility tradeoff. Furthermore, the amount
of noise necessary if many ghost users are created might be too large.}

\lyt{Note that the application can also store this information if it wants...}
\fi
